Notes for ISIPTA poster

### 2016-07-19 asce-paper.tex
Sec 4.4

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}

@@

The structure of complex systems can be visualized by reliability block diagrams,
an example is given in Figure~***.
Components are represented by boxes or nodes,
and the system works when a path from the left end to the right exists
which passes only through working components.
In a system with $n$ components, the state of the components can be expressed by the state vector
$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not.
The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
\cite{BP75}.
Most real-life systems are coherent,
which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
so system functioning cannot be improved by worse performance of one or more of its components.
Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.

@@

In calculating the system reliability using \eqref{eq:sysrel-survsign},
the component-specific predictive probabilities $P(C^k_t = l_k)$
need to use all information available at time $\tnow$,
which, in the Bayesian framework,
are given by the posterior predictive distribution 
$P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$, $l_k = 0, 1, \ldots, n_k-e_k$. %$k=1,\ldots, K$.
(Remember that $e_k$ type $k$ components have failed by $\tnow$,
such that there are at most $n_k-e_k$ working components at time $\tnow$.)
%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
This posterior predictive distribution is obtained as
\begin{linenomath*}
\begin{align}
\lefteqn{%
P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
 &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
                                  \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k
\label{eq:postpredtnow}
\end{align}
\end{linenomath*}
%
Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have
\begin{linenomath*}
\begin{align}
P(T^k \leq t \mid T^k > \tnow, \lambda_k)
 &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
 &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
\end{align}
\end{linenomath*}
%
With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \\
 &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}\times\\&\hspace*{27ex}
    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
    \times \\ & \hspace*{13ex}
    \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
\end{align}
\end{linenomath*}
%
The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
allowing us to solve the integral using the corresponding normalization constant.
We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{10ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
    \nkz + e_k + 1} 
\end{align}
\end{linenomath*}

%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
%and summands whith even $j$ are decreasing in $t$,
%while summands whith odd $j$ are increasing in $t$.
%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
%and so the probability that $l_k$ of them remain operational must decrease.

***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?

@@

***Set of priors $\MkZ$ defined by $(\nkz,\ykz) \in \PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$.

***We actually need to compute only those $P(C^k_t = l_k\mid \ldots)$ with $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.

%I would think that
%$\min / \max_{(\nkz,\ykz) \in \PkZ} P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$
%must be solved by numeric optimization for each $k, l_k, t$ 
%because of the alternating signs for the summands.
%(In absolute terms, each summand is increasing in $\ykz$, but not monotone in $\nkz$.)

%(Box-constraint optimization possible, e.g., with option \texttt{L-BFGS-B} of \texttt{optim} in \textbf{R}.)
Similar to the considerations about $t$, as higher values for $\ykz$ mean higher expected lifetimes for the components,
the larger $\ykz$, the higher the probability that many components survive
($P(C^k_t = l_k\mid\ldots)$ high for large $l_k$)
and, with that, the lower the probability that few or no components survive
($P(C^k_t = l_k\mid\ldots)$ low for small $l_k$).

In terms of the cumulative probability mass function (cmf) for $C^k_t$, which can be written as 
\begin{linenomath*}
\begin{align}
%F_{C^k_t}(l_k \mid \nkz,\ykz, \mbf{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) 
% = \sum_{q=0}^{l_k} P(C^k_t = q\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
\end{align}
\end{linenomath*}
we therefore conclude that
the lower cmf $\ul{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the lower bounds for all $\ykz$, $k=1,\ldots,K$,
and the upper cmf $\ol{F}(C^k_t = l_k\mid \ldots)$ must be obtained with the respective upper bounds.

***proove rigorously (would need a kind of likelihood difference order)?
%Do I get your comments right that based on lower and upper bounds
%$\ul{P}(C^k_t = l_k\mid \ldots)$ and $\ol{P}(C^k_t = l_k\mid \ldots)$ for all $l_k = 0, 1, \ldots, n_k - e_k$,
%we can easily get lower and upper bounds for the cdf $F_{C^k_t}(l_k \mid \ldots)$?

Furthermore, higher expected lifetimes for the components must mean
a longer system survival, so in turn the $\ul{F}_{C^k_t}(l_k \mid \ldots)$'s
should give us the lower bound for $P(\Tsys > t\mid\ldots)$,
and the $\ol{F}_{C^k_t}(l_k \mid \ldots)$'s the upper bound.
Note that e.g.\ $\ul{F}_{C^k_t}(l_k \mid \ldots)$ may, however, not correspond to a single parameter pair $(\nkz, \ykz)$.
Also, in the system survival equation ($t > \tnow$)
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)

Writing out Equation~\eqref{eq:25}, we get
\begin{linenomath*}
\begin{align}
\lefteqn{P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{45ex}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K \label{eq:30}
    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{17ex}
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
    \nkz + e_k + 1} 
\end{align}
\end{linenomath*}

While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.

@@

***from poster or similar

>>>>

\def\nkz{n\uz_k}
\def\nkn{n\un_k}
\newcommand{\nkzfun}[1]{n\uz_{#1}}
\newcommand{\nkzlfun}[1]{\ul{n}\uz_{#1}}
\newcommand{\nkzufun}[1]{\ol{n}\uz_{#1}}

@@

The structure of complex systems can be visualized by reliability block diagrams,
an example is given in Figure~\ref{fig:bridge-layout}.
Components are represented by boxes or nodes,
and the system works when a path from the left end to the right exists
which passes only through working components.
In a system with $n$ components, the state of the components can be expressed by the state vector
$\vec{x} = (x_1,x_2,\ldots,x_n) \in \{0,1\}^n$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not.
The structure function $\phi : \{0,1\}^n \rightarrow \{0,1\}$, defined for all possible $\vec{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\vec{x}$
\cite{BP75}.
Most real-life systems are coherent,
which means that $\phi(\vec{x})$ is non-decreasing in any of the components of $\vec{x}$,
so system functioning cannot be improved by worse performance of one or more of its components.
Furthermore, one can usually assume that $\phi(0, \ldots, 0) = 0$ and $\phi(1, \ldots, 1) = 1$.

@@

In calculating the system reliability using \eqref{eq:sysrel-survsign},
the component-specific predictive probabilities $P(C^k_t = l_k)$
need to use all information available at time $\tnow$,
which, in the Bayesian framework,
are given by the posterior predictive distribution 
$P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$, $l_k = 0, 1, \ldots, n_k-e_k$. %$k=1,\ldots, K$.
(Remember that $e_k$ type $k$ components have failed by $\tnow$,
such that there can be at most $n_k-e_k$ working components beyond time $\tnow$.)
%(Should one work with the subsystem consisting only of the non-failed $n_k - e_k$ components?)\\
This posterior predictive distribution is obtained as
\begin{linenomath*}
\begin{align}
\lefteqn{%
P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\  %
 &= { n_k - e_k \choose l_k} \int \big[P(T^k >    t \mid T^k > \tnow, \lambda_k)\big]^{l_k} \times \nonumber\\ & \hspace*{17ex}
                                  \big[P(T^k \leq t \mid T^k > \tnow, \lambda_k)\big]^{n_k - e_k - l_k}
    f(\lambda_k\mid\nkz,\ykz,\vec{t}^k_{e_k;n_k}) \dd \lambda_k
\label{eq:postpredtnow}
\end{align}
\end{linenomath*}
%
Now, by the Weibull assumption \eqref{eq:weibullcdf}, we have
\begin{linenomath*}
\begin{align}
P(T^k \leq t \mid T^k > \tnow, \lambda_k)
 &= \frac{P(\tnow < T^k \leq t \mid\lambda_k)}{P(T^k > \tnow \mid \lambda_k)} \nonumber\\
 &= \frac{F(t\mid\lambda_k) - F(\tnow\mid\lambda_k)}{1-F(\tnow\mid\lambda_k)} 
% = \frac{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}} - e^{-\frac{t^{\beta_k}}{\lambda_k}}}{e^{-\frac{(\tnow)^{\beta_k}}{\lambda_k}}}
  = 1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\,.
\end{align}
\end{linenomath*}
%
With this and the posterior \eqref{eq:ig-update-alpha} substituted into \eqref{eq:postpredtnow}, we get
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})}\hspace*{5ex} \nonumber\\
 &= { n_k - e_k \choose l_k} \int \Big[    e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{l_k}
                                  \Big[1 - e^{-\frac{t^{\beta_k} - (\tnow)^{\beta_k}}{\lambda_k}}\Big]^{n_k - e_k - l_k}
    \times \nonumber\\ & \hspace*{27ex}
    \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} \lambda_k^{-(\nkn + 1) - 1} e^{-\frac{\nkn\ykn}{\lambda_k}} \dd \lambda_k \nonumber\\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j} \frac{\big(\nkn\ykn\big)^{\nkn + 1}}{\Gamma(\nkn+1)} 
    \times \nonumber\\ & \hspace*{13ex}
    \int \lambda_k^{-(\nkn + 1) - 1} \exp\Big\{-\frac{(l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}) + \nkn\ykn}{\lambda_k}\Big\} \dd \lambda_k\,.
\end{align}
\end{linenomath*}
%
The terms remaining under the integral form the core of an inverse gamma distribution \eqref{eq:ig-def}
with parameters $\nkn + 1$ and $\nkn\ykn + (l_k + j) (t^{\beta_k} - (\tnow)^{\beta_k}))$,
allowing us to solve the integral using the corresponding normalization constant.
We thus have, for $l_k \in \{0,1,\ldots,n_k-e_k\}$,
\begin{linenomath*}
\begin{align}
\lefteqn{P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})} \nonumber\\
 &= { n_k - e_k \choose l_k} \sum_{j=0}^{n_k-e_k-l_k} (-1)^j { n_k - e_k - l_k \choose j}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!}   
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) \big(t^{\beta_k} - (\tnow)^{\beta_k}\big)}\right)^{\nkn + 1} \nonumber\\
 &= \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \nonumber\\ & \hspace*{10ex}  
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k)       (\tnow)^{\beta_k} }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^{\beta_k} + (n_k-e_k-l_k-j) (\tnow)^{\beta_k} + (l_k + j) t^{\beta_k} }\right)^{%
    \nkz + e_k + 1}.
\label{eq:postpred-priorparams}
\end{align}
\end{linenomath*}
%
These posterior predictive probabilities can also be expressed as a cumulative probability mass function (cmf) 
\begin{linenomath*}
\begin{align}
F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) = P(C^k_t \leq l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k}) 
 = \sum_{j=0}^{l_k} P(C^k_t = j \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})\,.
%F_{C^k_t}(l_k \mid \ldots) = P(C^k_t \leq l_k\mid\ldots) = \sum_{q=0}^{l_k} P(C^k_t = q\mid\ldots)\,,
\end{align}
\end{linenomath*}
%Seen as function in $t$, we see that $t$ appears $n_k-e_k-l_k+1$ times,
%once in each summand, in the denominator of the fraction powered to the $\nkn+1$,
%and summands whith even $j$ are decreasing in $t$,
%while summands whith odd $j$ are increasing in $t$.
%Nevertheless, in total $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$
%must be decreasing in $t$, as the remaining $n_k-e_k$ components continue to age,
%and so the probability that $l_k$ of them remain operational must decrease.

@@

Together with \eqref{eq:postpred-priorparams},
\eqref{eq:sysrel-survsign} allows us to calculate the system reliability $\Rsys(t\mid t>\tnow)$
for fixed prior parameters $(\nkz, \ykz)$, $k=1, \ldots, K$.
In Section~\ref{sec:modforsurpr}, we argued for using sets of priors $\MZ$,
which allow for vague and incomplete prior knowledge, and provide prior-data conflict sensitivity.
%
We will thus use, for each component type,
a set of priors $\MkZ$ defined by varying $(\nkz,\ykz)$ in a prior parameter set $\PkZ = [\nkzl,\nkzu] \times [\ykzl,\ykzu]$,
and we are interested in the bounds
%This leads to a set of system reliability functions with the bounds
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow) &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:lrsysdef}\\
\uRsys(t \mid t > \tnow) &= \max_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big)\,,
\label{eq:ursysdef}
\end{align}
\end{linenomath*}
where we surpress in notation that $\lRsys(t \mid t > \tnow)$ and $\uRsys(t \mid t > \tnow)$
depend on prior parameter sets and data.

\eqref{eq:lrsysdef} and \eqref{eq:ursysdef} seem to suggest that
a full $2K$-dimensional box-constraint optimization is necessary,
but this is not the case.
Remember that $\Phi(l_1,\ldots,l_k)$ from \eqref{eq:sysrel-survsign} is non-decreasing in each of its arguments $l_1,\ldots,l_K$,
so if there is stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$,
then there is, for each component type $k$,
a prior parameter pair in $\PkZ$ that minimizes system reliability, and
a prior parameter pair in $\PkZ$ that maximizes system reliability,
independently of the other component types. 
%such that system reliability is
%minimized by a distribution that gives most weight to low values of $l_k$, and
%maximized by a distribution that gives most weight to high values of $l_k$.
Indeed, stochastic dominance in $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ is provided for $\ykz$.
To see this, note that $\ykz$ gives the mean expected lifetime for type $k$ components.
Thus, higher values for $\ykz$ mean higher expected lifetimes for the components,
which in turn increases the probability that many components survive until time $t$,
and with it, decreases the propability of few or no components surviving,
so in total giving low probability weight for low values of $l_k$,
and high probability weight for high values of $l_k$. 
We therefore conclude that, for any fixed value of $\nkz$,
the lower bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzu$, and
the upper bound of $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for all $l_k$ is obtained with $\ykzl$.

***need formal first-order stochastic dominance in $\ykz$ result for $P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})$?
I have it for inverse gamma posterior $f(\lambda_k\mid \nkz,\ykz, \vec{t}^k_{e_k;n_k})$,
but not for posterior predictive***

However, there is no corresponding reasoning for $\nkz$,
such that different values of $\nkz$ may minimize (or maximize) $F(l_k \mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ at different $l_k$'s.
Therefore, the $\nkz$ values for lower and upper system reliability bounds are obtained by numeric optimization.
%
\iffalse %---------------------------
\begin{linenomath*}
\begin{align} \label{eq:25}
\lefteqn{%
P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \hspace*{10ex}\nonumber\\ 
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \vec{t}^k_{e_k;n_k})
\end{align}
\end{linenomath*}
we cannot simply plug in all the $\ul{P}(C^k_t = l_k\mid \ldots)$ %and $\ol{P}(C^k_t = l_k\mid \ldots)$
to get $\ul{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$, % and $\ol{P}(\Tsys > t\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k})$,
as the $\ul{P}(C^k_t = l_k\mid \ldots)$ could correspond to different $(\nkz,\ykz)$ for each $l_k$.
(It would give us a lower bound for $\ul{P}(\Tsys > t\mid\ldots)$, however, but it might be very coarse.)
%
While it is clear that the lower bounds for $\ykz$ will lead to the lower system survival function,
the role of $\nkz$ is not so clear.
We therefore resort to numerical optimization of \eqref{eq:25} over $\{\nkz, k=1,\ldots,K\}$
to obtain the lower bound for $P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)$.
\fi %---------------------------

Writing out \eqref{eq:sysrel-survsign}, we get
\begin{linenomath*}
\begin{align}
\lRsys(t \mid t > \tnow)
 &= \min_{\PZi{1},\ldots,\PZi{K}} \Rsys\big(t \mid t > \tnow, \cup_{k=1}^K \{\PkZ, \vec{t}^k_{e_k;n_k}\}\big) \nonumber\\
 &= \min_{\substack{\nkzfun{1} \in \left[\nkzlfun{1}, \nkzufun{1}\right]\\ \vdots\\ \nkzfun{K} \in \left[\nkzlfun{K}, \nkzufun{K}\right]}}
    \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K P(C^k_t = l_k\mid\nkz,\ykzl, \mbf{t}^k_{e_k;n_k})\,,
\end{align}
\end{linenomath*}
such that a $K$-dimensional box-constraint optimization is needed to obtain $\lRsys(t \mid t > \tnow)$.
The result for $\uRsys(t \mid t > \tnow)$ is completely analogous.
Computing time can furthermore be saved
by computing only those $P(C^k_t = l_k\mid \nkz,\ykz,\vec{t}^k_{e_k;n_k})$ for $l_k$'s for which $\Phi(l_1,\ldots,l_K) > 0$.

\iffalse %---------------------------
\begin{linenomath*}
\begin{align}
\lefteqn{P(\Tsys > t\mid\{\nkz,\ykz, \mbf{t}^k_{e_k;n_k}\}_{k=1}^K)} \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    P(C^k_t = l_k\mid\nkz,\ykz, \mbf{t}^k_{e_k;n_k}) \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K
    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{45ex}
    \left(\frac{\nkn\ykn}{\nkn\ykn + (l_k + j) (t^\kappa - (\tnow)^\kappa)}\right)^{\nkn + 1} \\
 &= \sum_{l_1=0}^{n_1-e_1} \cdots \sum_{l_K=0}^{n_K-e_K} \Phi(l_1,\ldots,l_K) \prod_{k=1}^K \label{eq:30}
    \sum_{j=0}^{n_k-e_k-l_k} (-1)^j \frac{(n_k - e_k)!}{l_k! j! (n_k - e_k - l_k - j)!} \times \\ & \hspace*{17ex}
    \left(\frac{\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k) (\tnow)^\kappa }%
               {\nkz\ykz + \sum_{i=1}^{e_k} (t_i^k)^\kappa + (n_k-e_k-l_k-j) (\tnow)^\kappa + (l_k + j) t^\kappa }\right)^{%
    \nkz + e_k + 1} 
\end{align}
\end{linenomath*}
\fi %---------------------------

@@

***from poster, bridge type system Fig.~\ref{fig:bridge-layout}, or brake system from ijar paper?

we use box-constraint optimization with option \texttt{L-BFGS-B} of \texttt{optim} in \textsf{R}.

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T3)   at ( 5.6, 0) {T3};
\node[type2] (T2)   at ( 2.8, 0) {T2};
\node[type3] (T1-2) at ( 1.4, 1) {T1};
\node[type3] (T1-3) at ( 1.4,-1) {T1};
\node[type3] (T1-5) at ( 4.2, 1) {T1};
\node[type3] (T1-6) at ( 4.2,-1) {T1};
\coordinate (start) at (0  ,0);
\coordinate (end)   at (6.3,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (bista)     edge[hv path] (start)
                  edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (biend)     edge[vh path] (T1-5.east)
                  edge[vh path] (T1-6.east)
                  edge[hv path] (T3.west)
      (T3.east)   edge[hv path] (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' system with three component types.}
\label{fig:bridge-layout}
\end{figure}
